---
title: "COVID Transmission and Death Rates in the Philippines"
author: "Kenneth Fajardo"
date: "6/9/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Overview
This presentation demonstrates the use of the Plot.ly package in R. The data that we will be using here is the COVID data made available by [Our World In Data]("https://raw.githubusercontent.com/owid/covid-19-data/master/
public/data/owid-covid-data.csv"), focusing on COVID activity in the Philippines, as of 2021-06-08.

## Initialization
Load the needed libraries
```{r lib, message=FALSE}
library(plotly) # for generating interactive maps
library(dplyr) # for transforming data
library(tidyr) # for melting data
library(lubridate) # for coercing dates
```

Download the data.
```{r dl, eval=FALSE}
download.file("https://raw.githubusercontent.com/owid/covid-19-data/
              master/public/data/owid-covid-data.csv", "covid.csv")
```

Read the data.
```{r read}
covid <- read.csv("covid.csv")
```

***
Select columns describing new cases and new deaths in the Philippines. Transform date from factor to Date class.
```{r total, message=FALSE}
covid <- covid[,grep("new_cases$|new_deaths$|iso|date", 
                     names(covid))]
covid <- covid %>% filter(iso_code=="PHL") %>%
            mutate(date = ymd(date)) %>% select(-c(iso_code))
```

## Generate plot
**COVID Transmission and Death Rates in the Philippines as of 2021-06-08**
```{r geodata, echo=FALSE, message=FALSE, comment="", warning=FALSE}
plotx <- covid %>% gather("var", "value", -date) 
plot_ly(plotx, x=~date, y=~value, color=~var, type="scatter", mode="lines")